\chapter*{Reference} 
\addcontentsline{toc}{chapter}{Reference}
\label{Reference} 


\begin{itemize}

\item[1] Shaojie Bai, J Zico Kolter, and Vladlen Koltun. An Empirical Evaluation of Generic Convolutional and Recurrent Networks for Sequence Modeling. arXiv preprint arXiv:1803.01271, 2018.
\item[2] Alberto Gasparin, Slobodan Lukovic and Cesare Alippi.Deep Learning for Time Series Forecasting: The Electric Load Case.  arXiv:1907.09207, 2019. 
\item[3] Thomas Schlegl, Philipp Seebock, Sebastian M. Waldstein,
Ursula Schmidt-Erfurth, and Georg Lang. Unsupervised Anomaly Detection with Generative Adversarial Networks to Guide Marker Discovery. arXiv:1703.05921, 2017. 
\item[4] Karim Guirguis, Christoph Schorn, Andre Guntoro, Sherif Abdulatif, and Bin Yang. SELD-TCN: Sound Event Localization & Detection via Temporal Convolutional Networks. arXiv:2003.01609. 2020.
\item[5] Rui Dai, Shenkun Xu, Qian Gu, Chenguang Ji, and Kaikui Liu. Hybrid Spatio-Temporal Graph Convolutional Network: Improving Traffic Prediction with Navigation Data. arXiv:2006.12715.2020 .
\item[6] Hongyan Hao, Yan Wang, Yudi Xia, Furao Shen and Jian Zhao. Temporal Convolutional Attention-based Network For Sequence Modeling. arXiv:2002.12530. 2020.
\item[7] Colin Lea, Michael D. Flynn, Ren´e Vidal, Austin Reiter and Gregory D. Hager. Temporal Convolutional Networks for Action Segmentation and Detection. arXiv:1611.05267. 2016.
\item[8] Jining Yan, Lin Mu, Lizhe Wang, Rajiv Ranjan and Albert Y. Zomaya. Temporal Convolutional Networks for the Advance Prediction of ENSO. Nature Scientfic reports 8055. 2020.
\item[9] Shumin Deng, Ningyu Zhang, Wen Zhang, Jiaoyan Chen, Jeff Z. Pan and Huajun Chen. Knowledge-Driven Stock Trend Prediction and Explanation via Temporal Convolutional Network. WWW-19: Companion Proceedings of The 2019 World Wide Web Conference, p678–685. 2019.
\item[10] Yitian Chen, Yanfei Kang, Yixiong Chen and Zizhuo Wang. Probabilistic Forecasting with Temporal Convolutional Neural Network. arXiv:1906.04397. 2020.
\item[11] Dominique T. Shipmon, Jason M. Gurevitch, Paolo M. Piselli and Steve Edwards. Time Series Anomaly Detection; Detection of anomalous drops with limited features and sparse examples in noisy highly periodic data. arXiv:1708.\\03665. 2017.
\item[12] Yaguang Li, Rose Yu, Cyrus Shahabi and Yan Liu. Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting. arXiv:1707.01926. 2017.
\newpage
\thispagestyle{plain}

\item[13] Bin Zhou, Shenghua Liu, Bryan Hooi, Xueqi Cheng, Jing Ye. BeatGAN: Anomalous Rhythm Detection using Adversarially Generated Time Series. IJCAI-19, p4433-4439. 2019.
\item[14] Rethage, Dario, Jordi Pons, and Xavier Serra. A wavenet for speech denoising. arXiv:1706.07162. 2017.

\end{itemize}
